---
title: "Bullet Scan Examples"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
```

## Breakoff
This is a goldilocks problem - we want to see some breakoff at the bottom, but  we also want a good amount of striae. Scans 1-2 have not enough striae and no breakoff; scans 3-5 have mostly breakoff and very little striae. 
```{r, include = T}
list.files(file.path("figure", "problem_scans", "breakoff_issues"), full.names = T) %>%
knitr::include_graphics()
```

## Groove Engraved Areas
GEAs are narrower than Land engraved areas (LEAs).
```{r, include = T}
list.files(file.path("figure", "problem_scans", "gea_scans"), full.names = T) %>%
knitr::include_graphics()
```

## Misaligned

Alignment is also important - the bullet should not be tilted one way or another. 
```{r, include = T}
list.files(file.path("figure", "problem_scans", "misaligned_on_scope"), full.names = T) %>%
knitr::include_graphics()
```

## Tank rash or pitting

This probably can't be completely helped, as it's an artifact of the bullet itself, but here's what it looks like anyways:

```{r, include = T}
list.files(file.path("figure", "problem_scans", "tankrash_or_pitting"), full.names = T) %>%
knitr::include_graphics()
```



## Good scans 

```{r, include = T}
list.files(file.path("figure", "good_scans", "good"), full.names = T, recursive = T) %>%
  knitr::include_graphics()

```
